---
title: "LMM for experiment in Ubatuba 2018: revision Oecologia 2021"
author: "ALPS"
date: "8/5/2020"
output: html_document
editor_options: 
  chunk_output_type: console
chunk_output_type: console
---

#### Loading packages
```{r}

library(ggplot2)
library(ggpubr)
library(dplyr)
library(openxlsx) 
library(readxl)
library(dplyr)
library(plyr)
library(forcats)
library(tidyverse)
library(grid)
#source("borders_for_ggplot.r")
library(lme4)
library(nlme)
library(lmerTest)
library(bbmle)
library(ggeffects)
library(effects)
library(glmmTMB)
library(DHARMa)

setwd("~/Desktop/Chapter 2/submission/Oecologia/Review-9-21")
```

#### LMM for effect of density of prey and wave fetch (wave exposure)
```{r PCIS}

PCIS = read_excel("Pardal-2021-ubatuba-exp-Oecologia.xlsx", sheet = 2)
str(PCIS)

PCIS$site = as.factor(PCIS$site)
PCIS$preyDensity = as.factor(PCIS$preyDensity)
PCIS$wf_mean = as.numeric(PCIS$wf_mean)
PCIS$PCIS_final = as.numeric(PCIS$PCIS_final)

str(PCIS)

hist(PCIS$PCIS_final)

#### *** Verify homogeneity of variances per stratum *** ####
a0 = gls((PCIS_final) ~ preyDensity*wf_mean, method = "REML", data = PCIS)
plot(a0)## Evidence of unequal variances ##

a1 = gls((PCIS_final) ~ preyDensity*wf_mean, method = "REML", weights = varIdent(form=~1|preyDensity*wf_mean), data = PCIS)
a2 = gls((PCIS_final) ~ preyDensity*wf_mean, method = "REML", weights = varIdent(form=~1|preyDensity), data = PCIS)
a3 = gls((PCIS_final) ~ preyDensity*wf_mean, method = "REML", weights = varIdent(form=~1|wf_mean), data = PCIS)

m = list(a0, a1, a2, a3) ## list of models under comparison ##
modnames.m = c("a0", "a1", "a2", "a3") ## naming different models ##
AICctab(m, mnames= modnames.m, base=TRUE, weights=TRUE, logLik=TRUE) ## AICc tab ##

anova(a2, a0)
plot(a2)
## Result: heterocedasticity; therefore consider model that account for that ##

#### *** LMM: pcis ~ prey density*wave exposure and random effect of site *** ####
m.pcis = lme(PCIS_final ~ preyDensity*site, random = ~1|site, data = PCIS)

plot(resid(m.pcis, type = "pearson") ~ fitted(m.pcis)) ## evidence of unequal variances ##
plot(resid(m.pcis, type = "pearson") ~ PCIS$wf_mean) ## OK ##
plot(resid(m.pcis, type = "pearson") ~ PCIS$preyDensity) ## different variance by treatment ##

m.pcis1  = lme(PCIS_final ~ preyDensity*wf_mean, random = ~1|site, weights = varIdent(form = ~1|preyDensity*wf_mean), data = PCIS)
m.pcis1b = lme(PCIS_final ~ preyDensity*wf_mean, random = ~1|site, weights = varIdent(form = ~1|preyDensity), data = PCIS)
m.pcis1c = lme(PCIS_final ~ preyDensity*wf_mean, random = ~1|site, weights = varPower(form = ~wf_mean), data = PCIS)

m2 = list(m.pcis, m.pcis1, m.pcis1b, m.pcis1c, a2) ## list of models under comparison ##
modnames.m2 = c("m.pcis","m.pcis1", "m.pcis1b", "m.pcis1c", "a2") ## naming different models ##
AICctab(m2, mnames= modnames.m2, base=TRUE, weights=TRUE, logLik=TRUE) ## AICc tab ##

summary(m.pcis1b)
anova(m.pcis1b)

plot(m.pcis1b)
hist(resid(m.pcis1b))
VarCorr(m.pcis1b)

lm.MANp = lm(PCIS_final ~ wf_mean, data = droplevels(subset(PCIS, !(preyDensity == "ambient"))))
summary(lm.MANp)

lm.AMBp = lm(PCIS_final ~ wf_mean, data = droplevels(subset(PCIS, !(preyDensity == "manipulated"))))
summary(lm.AMBp)

## Correcting P-value:
p = c(5.44e-05, 0.011697)
p.adjust(p, method = c("bonferroni"))
#p.adjust(p, method = c("fdr"))

## Conclusion: PCIS60 increases with wave exposure (i.e., IS gets weaker) but with different rates depending on prey density ##
```

#### Plotting PCIS ~ prey density treatment
```{r}

predPCIS = PCIS ## Dataframe for predictions ##
predPCIS = subset(predPCIS, select = c(1, 2, 12, 17)) ## keep only useful columns ##
predPCIS$wf_mean2 = as.character(predPCIS$wf_mean) ## create character column to match ##
predPCIS1 = droplevels(subset(predPCIS, !(preyDensity == "manipulated")))

mydfAMB = ggeffect(m.pcis1b, terms = c("preyDensity[ambient]", "wf_mean"))
names(mydfAMB) <- c("preyDensity", "predicted", "sd", "low", "high", "wf_mean") ## renaming output ##

predPCIS1$predicted  <- mydfAMB$predicted[match(as.character(predPCIS1$wf_mean2), as.factor(mydfAMB$wf_mean))]
predPCIS1$low        <- mydfAMB$low[match(as.character(predPCIS1$wf_mean2), as.factor(mydfAMB$wf_mean))]
predPCIS1$high       <- mydfAMB$high[match(as.character(predPCIS1$wf_mean2), as.factor(mydfAMB$wf_mean))]


predPCIS2 = droplevels(subset(predPCIS, !(preyDensity == "ambient")))

mydfMAN = ggeffect(m.pcis1b, terms = c("preyDensity[manipulated]", "wf_mean"))
names(mydfMAN) <- c("preyDensity", "predicted", "sd", "low", "high", "wf_mean") ## renaming output ##

predPCIS2$predicted  <- mydfMAN$predicted[match(as.character(predPCIS2$wf_mean2), as.factor(mydfMAN$wf_mean))]
predPCIS2$low        <- mydfMAN$low[match(as.character(predPCIS2$wf_mean2), as.factor(mydfMAN$wf_mean))]
predPCIS2$high       <- mydfMAN$high[match(as.character(predPCIS2$wf_mean2), as.factor(mydfMAN$wf_mean))]

predPCIS <-rbind(predPCIS1, predPCIS2)
rm(predPCIS1, predPCIS2)

levels(predPCIS$preyDensity) <- c("ambient", "reduced")

pcis_fig=
ggplot(predPCIS, aes(x = wf_mean, 
                     y = PCIS_final, 
                     color = preyDensity, 
                     shape = preyDensity)) +
     geom_ribbon(aes(ymin = low, 
                     ymax = high, 
                     fill = preyDensity),
                 alpha = .3) +
     scale_fill_manual(values=c("grey80", "grey80")) +
     geom_line(aes(y = predicted, linetype = preyDensity), 
               size = 1.1) +
     scale_linetype_manual(values= c("solid", "solid"))+
     geom_point(size= 2.6, 
                alpha=0.95) + 
     scale_shape_manual(values=c(15, 1))+
     scale_color_manual(values=c('black','black')) +
     theme_classic() +
     theme(axis.text.x = element_text(size=14, color="black"), 
           axis.text.y = element_text(size=14, color="black"),
           axis.title.x = element_text(color="black", size=16.),
           axis.title.y = element_text(color="black", size=16)) +
     labs(x = expression(paste("wave fetch (log"[10]," no. of cells)")),
          y = "PCIS") +
     theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
     theme(axis.line = element_line(colour = 'black', size = 0.8)) +
     theme(axis.ticks.length = unit(4, "pt")) +
     theme(legend.position = c(.02, .93),
           legend.justification = c("left"),
           legend.box.just = "left",
           legend.margin = margin(0, 0, 0, 0),
           legend.key.size = unit(1.5,"line")) +
     theme(legend.title = element_text(color = "white", size = 5),
           legend.text = element_text(color = "black", size=11))+
     theme(plot.margin=unit(c(0.2, .2, 0.2, 0.2), "cm")) + coord_cartesian(xlim = c(2.3, 3.7))

pcis_fig 
```

#### Residuals for PCIS model: PCIS ~ prey density treatment
```{r}
res.pcis1 = residuals(m.pcis1b, type = "normalized") ## to get residuals of the model ##
fit.pcis1 = fitted(m.pcis1b) ## to get fitted valies  of the model ##

res.pcis1 = cbind(res.pcis1, fit.pcis1) ## binding columns ##
res.pcis1 = as.data.frame(res.pcis1) ## transforming objetc in dataframe ##

res.pcis1$preyDensity = PCIS$preyDensity ## getting column time from dataframe with same length ##
res.pcis1$wf_mean     = PCIS$wf_mean ## getting column tr from dataframe with same length ##

levels(res.pcis1$preyDensity) <- c("ambient", "reduced")

res.1 = ggplot(res.pcis1, aes(x=fit.pcis1, y=res.pcis1)) + theme_linedraw()+ geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),axis.title.y = element_text(color="black", size=14))+
  labs(x = "fitted values", y = "normalised residuals") +
  theme(strip.text.x = element_text(size = 12), strip.text.y = element_text(size = 12))+
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ theme(plot.margin = unit(c(0.15,0.30,0.15,.15), "lines")) +
  theme(strip.text.x = element_text(size = 10), strip.text.y = element_text(size = 10))+
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.1b = ggplot(res.pcis1, aes(x=wf_mean, y=res.pcis1)) + theme_linedraw()+ geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),axis.title.y = element_text(color="black", size=14))+
  labs(x = "wave fetch", y = "normalised residuals") +
  theme(strip.text.x = element_text(size = 12), strip.text.y = element_text(size = 12))+
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ theme(plot.margin = unit(c(0.15,0.15,.15,.15), "lines")) +
  theme(strip.text.x = element_text(size = 10), strip.text.y = element_text(size = 10))+
  #scale_x_continuous(breaks = c(0, 30,60,90))+
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.2 = ggplot(res.pcis1, aes(x=preyDensity, y=res.pcis1)) + theme_linedraw()+ geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),axis.title.y = element_text(color="black", size=14))+
  labs(x = "prey density treatment", y = "normalised residuals") +
  theme(strip.text.x = element_text(size = 12), strip.text.y = element_text(size = 12))+
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ theme(plot.margin = unit(c(0.15,0.15,.3,.15), "lines")) +
  theme(strip.text.x = element_text(size = 10), strip.text.y = element_text(size = 10))+
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.3 = ggplot(res.pcis1, aes(x=res.pcis1)) + geom_histogram(color="black", fill="white", bins=8)+ theme_linedraw()+
  theme(axis.text.x = element_text(size=12, color="black"), axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),axis.title.y = element_text(color="black", size=14))+
  labs(x = "normalised residuals", y = "count") +
  theme(strip.text.x = element_text(size = 12), strip.text.y = element_text(size = 12))+
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ theme(plot.margin = unit(c(1.2,0.15,0.15,.15), "lines")) +
  theme(strip.text.x = element_text(size = 10), strip.text.y = element_text(size = 10))+
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

r.pcis = ggarrange(res.1, res.1b, res.2, res.3, ncol = 2, nrow = 2, align = "hv")
r.pcis = annotate_figure(r.pcis, fig.lab = "PCIS", fig.lab.face = "bold", fig.lab.size=12)
r.pcis

ggsave("residuals_pcis_final.png", dpi = 300, width = 5.82, height = 6.01, units = "in")
varhandle::rm.all.but(c("pcis_fig"))

```


#### Models for consumption rate (effect of prey density and mean wave fetch)
```{r Consumption rate right}

pcis = read_excel("Pardal-2021-ubatuba-exp-Oecologia.xlsx", sheet = 3)
str(pcis)

pcis$site = as.factor(pcis$site)
pcis$preyDensity = as.factor(pcis$preyDensity)
pcis$wf_mean = as.numeric(pcis$wf_mean)
pcis$consRate = as.numeric(pcis$consRate)

str(pcis)

## important: consRate negatives values turned to 0 (there cannot be negative consumprion rate):
pcis$consRate[pcis$consRate < 0] = 0

hist(pcis$consRate)

#### *** Verify homogeneity of variances per stratum *** ####
b0 = gls(consRate ~ preyDensity*wf_mean, method = "REML", data = pcis)
b1 = gls(consRate ~ preyDensity*wf_mean, method = "REML", weights = varIdent(form=~1|preyDensity*wf_mean), data = pcis)
b2 = gls(consRate ~ preyDensity*wf_mean, method = "REML", weights = varIdent(form=~1|preyDensity), data = pcis)
b3 = gls(consRate ~ preyDensity*wf_mean, method = "REML", weights = varIdent(form=~1|wf_mean), data = pcis)

m3 = list(b0, b1, b2, b3)
modnames.m3 = c("b0", "b1", "b2", "b3")
AICctab(m3, mnames = modnames.m3, base =TRUE, weights =TRUE, logLik = TRUE) 

anova(b2, b0)
summary(b2)
plot(b2)
## Result: heterocedasticity per treatment stratum; therefore fit model that account for that ##

#### *** LMM: number of consumed barnacles ~ prey density*wave exposure *** ####

m.cons = lme(consRate ~ preyDensity*wf_mean, random = ~ 1|site, data = pcis)
plot(m.cons)

m.cons1 = lme(consRate ~ preyDensity*wf_mean, random = ~ 1|site, weights = varIdent(form=~1|preyDensity), data = pcis)
plot(m.cons1)
summary(m.cons1)
VarCorr(m.cons1)

### Separated LM per preyDensity:
lm.MAN = lm(consRate ~ wf_mean, data = droplevels(subset(pcis, !(preyDensity == "ambient"))))
summary(lm.MAN)
plot(lm.MAN)
hist(resid(lm.MAN))

lm.AMB = lm(consRate ~ wf_mean, data = droplevels(subset(pcis, !(preyDensity == "manipulated"))))
summary(lm.AMB)
hist(resid(lm.AMB))

p2 = c(7.92e-07, 0.3710)
p.adjust(p2, method = c("bonferroni"))
#p.adjust(p2, method = c("fdr"))

```


#### Plotting model with predictions
```{r}

predCons = pcis ## Dataframe for predictions ##
predCons = subset(predCons, select = c(1, 2, 12, 17)) ## keep only useful columns ##
predCons$wf_mean2 = as.character(predCons$wf_mean) ## create character column to match ##
predCons1 = droplevels(subset(predCons, !(preyDensity == "manipulated")))

mydf2AMB = ggeffect(m.cons1, terms = c("preyDensity[ambient]", "wf_mean"))
names(mydf2AMB) <- c("preyDensity", "predicted", "sd", "low", "high", "wf_mean") ## renaming output ##

predCons1$predicted  <- mydf2AMB$predicted[match(as.character(predCons1$wf_mean2), as.factor(mydf2AMB$wf_mean))]
predCons1$low        <- mydf2AMB$low[match(as.character(predCons1$wf_mean2), as.factor(mydf2AMB$wf_mean))]
predCons1$high       <- mydf2AMB$high[match(as.character(predCons1$wf_mean2), as.factor(mydf2AMB$wf_mean))]


predCons2 = droplevels(subset(predCons, !(preyDensity == "ambient")))

mydf2MAN = ggeffect(m.cons1, terms = c("preyDensity[manipulated]", "wf_mean"))
names(mydf2MAN) <- c("preyDensity", "predicted", "sd", "low", "high", "wf_mean") ## renaming output ##

predCons2$predicted  <- mydf2MAN$predicted[match(as.character(predCons2$wf_mean2), as.factor(mydf2MAN$wf_mean))]
predCons2$low        <- mydf2MAN$low[match(as.character(predCons2$wf_mean2), as.factor(mydf2MAN$wf_mean))]
predCons2$high       <- mydf2MAN$high[match(as.character(predCons2$wf_mean2), as.factor(mydf2MAN$wf_mean))]

predCons <-rbind(predCons1, predCons2)
rm(predCons1, predCons2)

levels(predCons$preyDensity) <- c("ambient", "reduced")

cons_fig=
ggplot(predCons, aes(x = wf_mean, y = consRate, color = preyDensity, shape = preyDensity)) +
     geom_ribbon(aes(ymin = low, ymax = high, fill = preyDensity), alpha = .3) +
     scale_fill_manual(values=c("grey80", "grey80")) +
     geom_line(aes(y = predicted, linetype = preyDensity), size = 1.1) +
     scale_linetype_manual(values= c("solid", "solid"))+
     geom_point(size= 2.5, alpha=0.95) + 
     scale_shape_manual(values=c(15,1))+
     scale_color_manual(values=c('black','black')) +
     theme_classic() +
     theme(axis.text.x = element_text(size=14, color="black"), 
           axis.text.y = element_text(size=14, color="black"),
           axis.title.x = element_text(color="black", size=16.),
           axis.title.y = element_text(color="black", size=16)) +
     labs(x = expression(paste("wave fetch (log"[10]," no. of cells)")),
          y = expression(atop("consumption rate", paste("(barnacles .whelk"^-1, ".day"^-1,")")))) +
     theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
     theme(axis.line = element_line(colour = 'black', size = 0.8)) +
     theme(axis.ticks.length = unit(4, "pt")) +
     theme(legend.position = c(.02, .93),
           legend.justification = c("left"),
           legend.box.just = "left",
           legend.margin = margin(0, 0, 0, 0),
           legend.key.size = unit(1.5,"line")) +
     theme(legend.title = element_text(color = "white", size = 5),
           legend.text = element_text(color = "black", size=11))+
     theme(plot.margin=unit(c(0.2, .2, 0.2, 0.2), "cm")) + coord_cartesian(xlim = c(2.3, 3.7))
cons_fig

ggarrange(cons_fig, pcis_fig, ncol = 2, nrow = 1, align = "hv")

ggsave("ubatuba18-final-rev4.svg", dpi = 500, height = 4.4, width = 12.7, units = "in")## Saving 12.7 x 4.4 in image 
```


##### Plotting residuals consumption model (consumption RATE ~ prey density treatment*wave fetch)
```{r}
res.cons2 = residuals(m.cons1, type = "normalized") ## to get residuals of the model ##
fit.cons2 = fitted(m.cons1) ## to get fitted valies  of the model ##

res.cons2 = cbind(res.cons2, fit.cons2) ## binding columns ##
res.cons2 = as.data.frame(res.cons2) ## transforming objetc in dataframe ##

res.cons2$preyDensity = pcis$preyDensity ## getting column time from dataframe with same length ##
res.cons2$wf_mean     = pcis$wf_mean ## getting column tr from dataframe with same length ##

levels(res.cons2$preyDensity) <- c("ambient", "reduced")

res.5 = ggplot(res.cons2, aes(x=fit.cons2, y=res.cons2)) + theme_linedraw()+ geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),axis.title.y = element_text(color="black", size=14))+
  labs(x = "fitted values", y = "normalised residuals") +
  theme(strip.text.x = element_text(size = 12), strip.text.y = element_text(size = 12))+
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ theme(plot.margin = unit(c(0.15,0.30,0.15,.15), "lines")) +
  theme(strip.text.x = element_text(size = 10), strip.text.y = element_text(size = 10))+
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.6 = ggplot(res.cons2, aes(x=wf_mean, y=res.cons2)) + theme_linedraw()+ geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),axis.title.y = element_text(color="black", size=14))+
  labs(x = "wave fetch", y = "normalised residuals") +
  theme(strip.text.x = element_text(size = 12), strip.text.y = element_text(size = 12))+
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ theme(plot.margin = unit(c(0.15,0.15,.15,.15), "lines")) +
  theme(strip.text.x = element_text(size = 10), strip.text.y = element_text(size = 10))+
  #scale_x_continuous(breaks = c(0, 30,60,90))+
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.7 = ggplot(res.cons2, aes(x=preyDensity, y=res.cons2)) + theme_linedraw()+ geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),axis.title.y = element_text(color="black", size=14))+
  labs(x = "prey density treatment", y = "normalised residuals") +
  theme(strip.text.x = element_text(size = 12), strip.text.y = element_text(size = 12))+
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ theme(plot.margin = unit(c(0.15,0.15,.3,.15), "lines")) +
  theme(strip.text.x = element_text(size = 10), strip.text.y = element_text(size = 10))+
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.8 = ggplot(res.cons2, aes(x=res.cons2)) + geom_histogram(color="black", fill="white", bins=8)+ theme_linedraw()+
  theme(axis.text.x = element_text(size=12, color="black"), axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),axis.title.y = element_text(color="black", size=14))+
  labs(x = "normalised residuals", y = "count") +
  theme(strip.text.x = element_text(size = 12), strip.text.y = element_text(size = 12))+
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ theme(plot.margin = unit(c(1.2,0.15,0.15,.15), "lines")) +
  theme(strip.text.x = element_text(size = 10), strip.text.y = element_text(size = 10))+
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

r1 = ggarrange(res.5, res.6, res.7, res.8, ncol = 2, nrow = 2, align = "hv")
r1 = annotate_figure(r1, fig.lab = "consumption rate", fig.lab.face = "bold", fig.lab.size=12)
r1

ggsave("residuals_consumption-rate-final.png", dpi = 300, width = 5.82, height = 6.01, units = "in")
```


#### BACKGROUND MORTALITY UBATUBA
```{r}

nat_mortality = read_excel("Pardal-2021-ubatuba-exp-Oecologia.xlsx", sheet= 1)
str(nat_mortality)


nat_mortality$site = as.factor(nat_mortality$site)
nat_mortality$preyDensity2 = as.factor(nat_mortality$preyDensity2)
nat_mortality$predTreat = as.factor(nat_mortality$predTreat)

str(nat_mortality)

nat_mortality$site = factor(nat_mortality$site, levels=c('Enseada','Lamberto', 'Lázaro',
                                                         'P. Grande', 'Maranduba', 'P. Vermelha', 
                                                         'Itaguá', 'Sta Rita', 'Fortaleza'))

str(nat_mortality)

mort3 = aggregate(mortNat ~ site +  + preyDensity, mean, data = nat_mortality)
mort4 = aggregate(mortNat ~ + preyDensity, mean, data = nat_mortality)


#dt2 =  ddply(nat_mortality, "preyDensity", transform, 
       #prey_mean  = mean(mortNat)) ## for plotting the global mean line ##

gexp1_back = ggplot(nat_mortality, aes(x = preyDensity2, y = mortNat, group= site))+ 
  theme_classic() +
  geom_point(
             size=2.3, 
             alpha=0.2) + 
  #geom_hline(aes(yintercept = prey_mean), 
   #          colour = 'gray', 
    #         linetype="dashed",
     #        size=1.2)+
  stat_summary(fun.data="mean_se",  
               fun.args = list(mult=1),
               geom="pointrange", 
               color = "black", 
               size=1.3)+
  facet_grid( ~ site, scale='free_y') +
  theme(axis.text.x = element_text(size=12, color="black"), 
                                   #angle= 90, 
                                   #vjust = 0.5,
                                   #hjust = 1),
        axis.text.y = element_text(size=12, color="black"), 
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "prey density treatment", 
       y = expression(atop("background mortality rate ", 
                          paste("(barnacles.day"^-1,")")))) +
  theme(strip.text.x = element_text(size = 12), 
        strip.text.y = element_text(size = 12))+
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))

#ggsave("Oecologia-back-mort-Ubatuba.svg", dpi = 300) 
```
