---
title:  "Experiment 1: Codes for LMMs and plots involving PCIS and Consumption rate ~ preyDensity*wave fetch"
author: "André Pardal"
date: "10 November 2021"
output: html_document
editor_options: 
  chunk_output_type: console
chunk_output_type: console
---

## Loading packages 
```{r Loading packages}

library(ggplot2)
library(ggpubr)
library(dplyr)
library(openxlsx) 
library(readxl)
library(dplyr)
library(plyr)
library(forcats)
library(tidyverse)
library(grid)
library(lme4)
library(nlme)
library(lmerTest)
library(bbmle)
library(ggeffects)
library(effects)
library(glmmTMB)
library(DHARMa)
library(httr)
library(tidytuesdayR)

setwd("~/Desktop/Chapter 2/submission/Oecologia/Review-9-21/Github/data")
```


## LMM for effect of density of prey and wave fetch (wave exposure)
```{r PCIS}

PCIS <- readxl::read_excel(temp_file, sheet = 5)

PCIS2 <- read_excel("Pardal-2021-data-Exp-01-Ubatuba.xlsx", sheet = 5)
str(PCIS)

PCIS$site        <- as.factor(PCIS$site)
PCIS$preyDensity <- as.factor(PCIS$preyDensity)
PCIS$wf_mean     <- as.numeric(PCIS$wf_mean)
PCIS$PCIS_final  <- as.numeric(PCIS$PCIS_final)

str(PCIS)

hist(PCIS$PCIS_final)

#### *** Verify homogeneity of variances per stratum *** ####
a0 <- gls((PCIS_final) ~ preyDensity*wf_mean, method = "REML", data = PCIS)
plot(a0)## Evidence of unequal variances ##

a1 <- gls((PCIS_final) ~ preyDensity*wf_mean, method = "REML", weights = varIdent(form = ~1|preyDensity*wf_mean), data = PCIS)
a2 <- gls((PCIS_final) ~ preyDensity*wf_mean, method = "REML", weights = varIdent(form = ~1|preyDensity), data = PCIS)
a3 <- gls((PCIS_final) ~ preyDensity*wf_mean, method = "REML", weights = varIdent(form = ~1|wf_mean), data = PCIS)

m          <- list(a0, a1, a2, a3) ## list of models under comparison ##
modnames.m <- c("a0", "a1", "a2", "a3") ## naming different models ##
AICctab(m, mnames= modnames.m, base=TRUE, weights=TRUE, logLik=TRUE) ## AICc tab ##

anova(a2, a0)
plot(a2)
## Result: heterocedasticity; therefore consider model that account for that ##

#### *** LMM: pcis ~ prey density*wave exposure and random effect of site *** ####
m.pcis <- lme(PCIS_final ~ preyDensity*site, random = ~1|site, data = PCIS)

plot(resid(m.pcis, type = "pearson") ~ fitted(m.pcis)) ## evidence of unequal variances ##
plot(resid(m.pcis, type = "pearson") ~ PCIS$wf_mean) ## OK ##
plot(resid(m.pcis, type = "pearson") ~ PCIS$preyDensity) ## different variance by treatment ##

m.pcis1  <- lme(PCIS_final ~ preyDensity*wf_mean, random = ~1|site, weights = varIdent(form = ~1|preyDensity*wf_mean), data = PCIS)
m.pcis1b <- lme(PCIS_final ~ preyDensity*wf_mean, random = ~1|site, weights = varIdent(form = ~1|preyDensity), data = PCIS)
m.pcis1c <- lme(PCIS_final ~ preyDensity*wf_mean, random = ~1|site, weights = varPower(form = ~wf_mean), data = PCIS)

m2          <- list(m.pcis, m.pcis1, m.pcis1b, m.pcis1c, a2) ## list of models under comparison ##
modnames.m2 <- c("m.pcis","m.pcis1", "m.pcis1b", "m.pcis1c", "a2") ## naming different models ##
AICctab(m2, mnames= modnames.m2, base=TRUE, weights=TRUE, logLik=TRUE) ## AICc tab ##

summary(m.pcis1b)
anova(m.pcis1b)

plot(m.pcis1b)
hist(resid(m.pcis1b))
VarCorr(m.pcis1b)

lm.MANp <- lm(PCIS_final ~ wf_mean, data = droplevels(subset(PCIS, !(preyDensity == "ambient"))))
summary(lm.MANp)

lm.AMBp <- lm(PCIS_final ~ wf_mean, data = droplevels(subset(PCIS, !(preyDensity == "manipulated"))))
summary(lm.AMBp)

## Correcting P-value:
p <- c(5.44e-05, 0.011697)
p.adjust(p, method = c("bonferroni"))

## Conclusion: PCIS increases with wave exposure (i.e., IS gets weaker) but with different rates depending on prey density ##
```


## Plotting PCIS ~ prey density treatment
```{r Predictions for PCIS}

predPCIS          <- PCIS ## Dataframe for predictions ##
predPCIS          <- subset(predPCIS, select = c(1, 2, 12, 17)) ## keep only useful columns ##
predPCIS$wf_mean2 <- as.character(predPCIS$wf_mean) ## create character column to match ##
predPCIS1         <- droplevels(subset(predPCIS, !(preyDensity == "manipulated")))

mydfAMB        <- ggeffect(m.pcis1b, terms = c("preyDensity[ambient]", "wf_mean"))
names(mydfAMB) <- c("preyDensity", "predicted", "sd", "low", "high", "wf_mean") ## renaming output ##

predPCIS1$predicted  <- mydfAMB$predicted[match(as.character(predPCIS1$wf_mean2), as.factor(mydfAMB$wf_mean))]
predPCIS1$low        <- mydfAMB$low[match(as.character(predPCIS1$wf_mean2), as.factor(mydfAMB$wf_mean))]
predPCIS1$high       <- mydfAMB$high[match(as.character(predPCIS1$wf_mean2), as.factor(mydfAMB$wf_mean))]

predPCIS2 = droplevels(subset(predPCIS, !(preyDensity == "ambient")))

mydfMAN        <- ggeffect(m.pcis1b, terms = c("preyDensity[manipulated]", "wf_mean"))
names(mydfMAN) <- c("preyDensity", "predicted", "sd", "low", "high", "wf_mean") ## renaming output ##

predPCIS2$predicted  <- mydfMAN$predicted[match(as.character(predPCIS2$wf_mean2), as.factor(mydfMAN$wf_mean))]
predPCIS2$low        <- mydfMAN$low[match(as.character(predPCIS2$wf_mean2), as.factor(mydfMAN$wf_mean))]
predPCIS2$high       <- mydfMAN$high[match(as.character(predPCIS2$wf_mean2), as.factor(mydfMAN$wf_mean))]

predPCIS <- rbind(predPCIS1, predPCIS2)
rm(predPCIS1, predPCIS2)

levels(predPCIS$preyDensity) <- c("ambient", "reduced")

pcis_fig <-
ggplot(predPCIS, aes(x = wf_mean, 
                     y = PCIS_final, 
                     color = preyDensity, 
                     shape = preyDensity)) +
     geom_ribbon(aes(ymin = low, 
                     ymax = high, 
                     fill = preyDensity),
                 alpha = .3) +
     scale_fill_manual(values=c("grey80", "grey80")) +
     geom_line(aes(y = predicted, linetype = preyDensity), 
               size = 1.1) +
     scale_linetype_manual(values= c("solid", "solid"))+
     geom_point(size= 2.6, 
                alpha=0.95) + 
     scale_shape_manual(values=c(15, 1))+
     scale_color_manual(values=c('black','black')) +
     theme_classic() +
     theme(axis.text.x = element_text(size=14, color="black"), 
           axis.text.y = element_text(size=14, color="black"),
           axis.title.x = element_text(color="black", size=16.),
           axis.title.y = element_text(color="black", size=16)) +
     labs(x = expression(paste("wave fetch (log"[10]," no. of cells)")),
          y = "PCIS") +
     theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
     theme(axis.line = element_line(colour = 'black', size = 0.8)) +
     theme(axis.ticks.length = unit(4, "pt")) +
     theme(legend.position = c(.02, .93),
           legend.justification = c("left"),
           legend.box.just = "left",
           legend.margin = margin(0, 0, 0, 0),
           legend.key.size = unit(1.5,"line")) +
     theme(legend.title = element_text(color = "white", size = 5),
           legend.text = element_text(color = "black", size=11))+
     theme(plot.margin=unit(c(0.2, .2, 0.2, 0.2), "cm")) + coord_cartesian(xlim = c(2.3, 3.7))

pcis_fig 
```


## Residuals for PCIS model: PCIS ~ prey density treatment
```{r Residuals plots}

res.pcis1 <- residuals(m.pcis1b, type = "normalized") ## to get residuals of the model ##
fit.pcis1 <- fitted(m.pcis1b) ## to get fitted valies  of the model ##

res.pcis1 <- cbind(res.pcis1, fit.pcis1) ## binding columns ##
res.pcis1 <- as.data.frame(res.pcis1) ## transforming objetc in dataframe ##

res.pcis1$preyDensity <- PCIS$preyDensity ## getting column time from dataframe with same length ##
res.pcis1$wf_mean     <- PCIS$wf_mean ## getting column tr from dataframe with same length ##

levels(res.pcis1$preyDensity) <- c("ambient", "reduced")

res.1 <-
  ggplot(res.pcis1, aes(x=fit.pcis1, y=res.pcis1)) + theme_linedraw()+ 
  geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "fitted values", 
       y = "normalised residuals") +
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(0.15,0.30,0.15,.15), "lines")) +
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.1b <-
  ggplot(res.pcis1, aes(x=wf_mean, y=res.pcis1)) + theme_linedraw()+ 
  geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "wave fetch", 
       y = "normalised residuals") +
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(0.15,0.15,.15,.15), "lines")) +
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.2 <-
  ggplot(res.pcis1, aes(x=preyDensity, y=res.pcis1)) + theme_linedraw() +
  geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "prey density treatment", 
       y = "normalised residuals") +
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(0.15,0.15,.3,.15), "lines")) +
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.3 <- 
  ggplot(res.pcis1, aes(x=res.pcis1)) + 
  geom_histogram(color="black", fill="white", bins=8)+ theme_linedraw()+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "normalised residuals", 
       y = "count") +
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(1.2,0.15,0.15,.15), "lines")) +
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

r.pcis <- ggarrange(res.1, res.1b, res.2, res.3, ncol = 2, nrow = 2, align = "hv")
r.pcis <- annotate_figure(r.pcis, fig.lab = "PCIS", fig.lab.face = "bold", fig.lab.size=12)
r.pcis

#ggsave("residuals_pcis_final.png", dpi = 300, width = 5.82, height = 6.01, units = "in")
varhandle::rm.all.but(c("pcis_fig"))
```


## Models for consumption rate (effect of prey density and mean wave fetch)
```{r Consumption rate }

CRdata <- read_excel("Pardal-2021-data-Exp-01-Ubatuba.xlsx", sheet = 6)
str(CRdata)

CRdata$site        <- as.factor(CRdata$site)
CRdata$preyDensity <- as.factor(CRdata$preyDensity)
CRdata$wf_mean     <- as.numeric(CRdata$wf_mean)
CRdata$consRate    <- as.numeric(CRdata$consRate)

str(CRdata)

## important: consRate negatives values turned to 0 (there cannot be negative consumprion rate):
CRdata$consRate[CRdata$consRate < 0] = 0

hist(CRdata$consRate)

## Verify homogeneity of variances per stratum ##
b0 <- gls(consRate ~ preyDensity*wf_mean, method = "REML", data = CRdata)
b1 <- gls(consRate ~ preyDensity*wf_mean, method = "REML", weights = varIdent(form=~1|preyDensity*wf_mean), data = CRdata)
b2 <- gls(consRate ~ preyDensity*wf_mean, method = "REML", weights = varIdent(form=~1|preyDensity), data = CRdata)
b3 <- gls(consRate ~ preyDensity*wf_mean, method = "REML", weights = varIdent(form=~1|wf_mean), data = CRdata)

m3          <- list(b0, b1, b2, b3)
modnames.m3 <- c("b0", "b1", "b2", "b3")
AICctab(m3, mnames = modnames.m3, base =TRUE, weights =TRUE, logLik = TRUE) 

anova(b2, b0)
summary(b2)
plot(b2)
## Result: heterocedasticity per treatment stratum; therefore fit model that account for that ##

## LMM: number of consumed barnacles ~ prey density*wave exposure ##

m.cons <- lme(consRate ~ preyDensity*wf_mean, random = ~ 1|site, data = CRdata)
plot(m.cons)

m.cons1 <- lme(consRate ~ preyDensity*wf_mean, random = ~ 1|site, weights = varIdent(form=~1|preyDensity), data = CRdata)
plot(m.cons1)
summary(m.cons1)
VarCorr(m.cons1)

### Separated LM per preyDensity:
lm.MAN <- lm(consRate ~ wf_mean, data = droplevels(subset(CRdata, !(preyDensity == "ambient"))))
summary(lm.MAN)
plot(lm.MAN)
hist(resid(lm.MAN))

lm.AMB <- lm(consRate ~ wf_mean, data = droplevels(subset(CRdata, !(preyDensity == "manipulated"))))
summary(lm.AMB)
hist(resid(lm.AMB))

p2 <- c(7.92e-07, 0.3710)
p.adjust(p2, method = c("bonferroni"))
#p.adjust(p2, method = c("fdr"))
```


## Plotting model with predictions ##
```{r Predictions for consumption rate}

predCons          <- CRdata ## Dataframe for predictions ##
predCons          <- subset(predCons, select = c(1, 2, 12, 17)) ## keep only useful columns ##
predCons$wf_mean2 <- as.character(predCons$wf_mean) ## create character column to match ##
predCons1         <- droplevels(subset(predCons, !(preyDensity == "manipulated")))

mydf2AMB        <- ggeffect(m.cons1, terms = c("preyDensity[ambient]", "wf_mean"))
names(mydf2AMB) <- c("preyDensity", "predicted", "sd", "low", "high", "wf_mean") ## renaming output ##

predCons1$predicted  <- mydf2AMB$predicted[match(as.character(predCons1$wf_mean2), as.factor(mydf2AMB$wf_mean))]
predCons1$low        <- mydf2AMB$low[match(as.character(predCons1$wf_mean2), as.factor(mydf2AMB$wf_mean))]
predCons1$high       <- mydf2AMB$high[match(as.character(predCons1$wf_mean2), as.factor(mydf2AMB$wf_mean))]


predCons2 <- droplevels(subset(predCons, !(preyDensity == "ambient")))

mydf2MAN        <- ggeffect(m.cons1, terms = c("preyDensity[manipulated]", "wf_mean"))
names(mydf2MAN) <- c("preyDensity", "predicted", "sd", "low", "high", "wf_mean") ## renaming output ##

predCons2$predicted  <- mydf2MAN$predicted[match(as.character(predCons2$wf_mean2), as.factor(mydf2MAN$wf_mean))]
predCons2$low        <- mydf2MAN$low[match(as.character(predCons2$wf_mean2), as.factor(mydf2MAN$wf_mean))]
predCons2$high       <- mydf2MAN$high[match(as.character(predCons2$wf_mean2), as.factor(mydf2MAN$wf_mean))]

predCons <-rbind(predCons1, predCons2)
rm(predCons1, predCons2)

levels(predCons$preyDensity) <- c("ambient", "reduced")

cons_fig <-
ggplot(predCons, aes(x = wf_mean, 
                     y = consRate, 
                     color = preyDensity, 
                     shape = preyDensity)) +
     geom_ribbon(aes(ymin = low, 
                     ymax = high, 
                     fill = preyDensity), 
                 alpha = .3) +
     scale_fill_manual(values=c("grey80", "grey80")) +
     geom_line(aes(y = predicted, linetype = preyDensity), size = 1.1) +
     scale_linetype_manual(values= c("solid", "solid"))+
     geom_point(size= 2.5, alpha=0.95) + 
     scale_shape_manual(values=c(15,1))+
     scale_color_manual(values=c('black','black')) +
     theme_classic() +
     theme(axis.text.x = element_text(size=14, color="black"), 
           axis.text.y = element_text(size=14, color="black"),
           axis.title.x = element_text(color="black", size=16.),
           axis.title.y = element_text(color="black", size=16)) +
     labs(x = expression(paste("wave fetch (log"[10]," no. of cells)")),
          y = expression(atop("consumption rate", paste("(barnacles .whelk"^-1, ".day"^-1,")")))) +
     theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
     theme(axis.line = element_line(colour = 'black', size = 0.8)) +
     theme(axis.ticks.length = unit(4, "pt")) +
     theme(legend.position = c(.02, .93),
           legend.justification = c("left"),
           legend.box.just = "left",
           legend.margin = margin(0, 0, 0, 0),
           legend.key.size = unit(1.5,"line")) +
     theme(legend.title = element_text(color = "white", size = 5),
           legend.text = element_text(color = "black", size=11))+
     theme(plot.margin=unit(c(0.2, .2, 0.2, 0.2), "cm")) + coord_cartesian(xlim = c(2.3, 3.7))

cons_fig

ggarrange(cons_fig, pcis_fig, ncol = 2, nrow = 1, align = "hv")

#ggsave("ubatuba18-final-rev4.svg", dpi = 500, height = 4.4, width = 12.7, units = "in")## Saving 12.7 x 4.4 in image 
```


### Plotting residuals consumption model (consumption RATE ~ prey density treatment*wave fetch) ##
```{r Residuals plots}

res.cons2 <- residuals(m.cons1, type = "normalized") ## to get residuals of the model ##
fit.cons2 <- fitted(m.cons1) ## to get fitted valies  of the model ##

res.cons2 <- cbind(res.cons2, fit.cons2) ## binding columns ##
res.cons2 <- as.data.frame(res.cons2) ## transforming objetc in dataframe ##

res.cons2$preyDensity = CRdata$preyDensity ## getting column time from dataframe with same length ##
res.cons2$wf_mean     = CRdata$wf_mean ## getting column tr from dataframe with same length ##

levels(res.cons2$preyDensity) <- c("ambient", "reduced")

res.5 <- 
  ggplot(res.cons2, aes(x=fit.cons2, y=res.cons2)) + theme_linedraw()+ 
  geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "fitted values", 
       y = "normalised residuals") +
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(0.15,0.30,0.15,.15), "lines")) +
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.6 <- 
  ggplot(res.cons2, aes(x=wf_mean, y=res.cons2)) + theme_linedraw()+ 
  geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "wave fetch", 
       y = "normalised residuals") +
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(0.15,0.15,.15,.15), "lines")) +
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.7 <- 
  ggplot(res.cons2, aes(x=preyDensity, y=res.cons2)) + theme_linedraw()+ 
  geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "prey density treatment", 
       y = "normalised residuals") +
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(0.15,0.15,.3,.15), "lines")) +
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.8 <- 
  ggplot(res.cons2, aes(x=res.cons2)) + 
  geom_histogram(color="black", fill="white", bins=8)+ theme_linedraw()+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "normalised residuals", 
       y = "count") +
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(1.2,0.15,0.15,.15), "lines")) +
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

r1 <- ggarrange(res.5, res.6, res.7, res.8, ncol = 2, nrow = 2, align = "hv")
r1 <- annotate_figure(r1, fig.lab = "consumption rate", fig.lab.face = "bold", fig.lab.size=12)
r1

#ggsave("residuals_consumption-rate-final.png", dpi = 300, width = 5.82, height = 6.01, units = "in")
```

## Other figures from Experiment 01:
## Initial density of barnacles (prey) in Ubatuba (Fig. 2 in the manuscript)
```{r Barnacle density time 0}

tetra_density <- read_excel("Pardal-2021-data-Exp-01-Ubatuba.xlsx", sheet = 7)

tetra_density$barnacles   <- as.numeric(tetra_density$barnacles)
tetra_density$site        <- as.factor(tetra_density$site)
tetra_density$preyDensity <- as.factor(tetra_density$preyDensity)
tetra_density$predTreat   <- as.factor(tetra_density$predTreat)

str(tetra_density)

tetra_density$site <- factor(tetra_density$site, levels=c('Enseada','Lamberto', 'Lázaro',
                                                         'P. Grande', 'Maranduba', 'P. Vermelha', 
                                                         'Itaguá', 'Sta Rita', 'Fortaleza'))

tetra_density <- tetra_density[!is.na(tetra_density$barnacles),]

dt <-  ddply(tetra_density, "preyDensity", transform, 
       prey_mean  = mean(barnacles)) ## for plotting the global mean line ##

barnacle_density <-
  ggplot(dt, aes(x = predTreat, 
                 y = barnacles, 
                 group= site))+ 
  theme_classic() +
  #geom_jitter(position=position_jitter(0.02), 
             #size=2.3, 
             #alpha=0.2) + 
  geom_hline(aes(yintercept = 
                   prey_mean), 
             colour = 'gray', 
             linetype="dashed",
             size=1.2)+
  stat_summary(fun.data="mean_se",  
               fun.args = list(mult=1),
               geom="pointrange", 
               color = "black", 
               size=1.3)+
  facet_grid(preyDensity ~ site, scale='free_y') +
  theme(axis.text.x = element_text(size=12, color="black"),
        axis.text.y = element_text(size=12, color="black"), 
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "treatment", 
       y = expression(paste("number of barnacles (ind.625 cm"^-2,")")))+
  theme(strip.text.x = element_text(size = 12), 
        strip.text.y = element_text(size = 12))+
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))

barnacle_density 

#ggsave("figs/Oecologia-density_initial.png", dpi = 400, width = 9.6, height = 5, units="in") 
```


## Backgroun mortality in Ubatuba (ESM: Appendix A: Fig. A5-A) 
```{r Plotting background mortality in Experiment 01}

nat_mortality <- read_excel("Pardal-2021-data-Exp-01-Ubatuba.xlsx", sheet= 4)
str(nat_mortality)

nat_mortality$site         <- as.factor(nat_mortality$site)
nat_mortality$preyDensity2 <- as.factor(nat_mortality$preyDensity2)
nat_mortality$predTreat    <- as.factor(nat_mortality$predTreat)

str(nat_mortality)

nat_mortality$site <- factor(nat_mortality$site, levels=c('Enseada','Lamberto', 'Lázaro',
                                                          'P. Grande', 'Maranduba', 'P. Vermelha', 
                                                          'Itaguá', 'Sta Rita', 'Fortaleza'))

str(nat_mortality)

mort3 <- aggregate(mortNat ~ site +  preyDensity, mean, data = nat_mortality)
mort4 <- aggregate(mortNat ~ + preyDensity, mean, data = nat_mortality)

#dt2 =  ddply(nat_mortality, "preyDensity", transform, 
       #prey_mean  = mean(mortNat)) ## for plotting the global mean line ##

figMort <-
  ggplot(nat_mortality, aes(x = preyDensity2, y = mortNat, group= site))+ 
  theme_classic() +
  geom_point(
             size=2.3, 
             alpha=0.2) + 
  #geom_hline(aes(yintercept = prey_mean), 
   #          colour = 'gray', 
    #         linetype="dashed",
     #        size=1.2)+
  stat_summary(fun.data="mean_se",  
               fun.args = list(mult=1),
               geom="pointrange", 
               color = "black", 
               size=1.3)+
  facet_grid( ~ site, scale='free_y') +
  theme(axis.text.x = element_text(size=12, color="black"), 
                                   #angle= 90, 
                                   #vjust = 0.5,
                                   #hjust = 1),
        axis.text.y = element_text(size=12, color="black"), 
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "prey density treatment", 
       y = expression(atop("background mortality rate ", 
                          paste("(barnacles.day"^-1,")")))) +
  theme(strip.text.x = element_text(size = 12), 
        strip.text.y = element_text(size = 12))+
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))

figMort
#ggsave("Oecologia-back-mort-Ubatuba.svg", dpi = 300) 
```
