---
title: "Experiment 2: Codes for LMMs and plots involving PCIS and Consumption rate ~ preyDensity*wave fetch"
author: "André Pardal"
date: "10 November 2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

##Loading packages ##
```{r loading packages}

library(ggplot2)
library(ggpubr)
library(dplyr)
library(openxlsx)  
library(readxl)
library(dplyr)
library(plyr)
library(forcats)
library(tidyverse)
library(grid)
library(xlsx)
library(writexl)
library(ggeffects)
library(nlme)

setwd("~/Desktop/Chapter 2/submission/Oecologia/Review-9-21/Github/data")
dir()
```


## LMM for effect of Chla and SST on PCIS ##
```{r PCIS}

PCIS_LE <- read_excel("Pardal-2021-data-Exp-02.xlsx", sheet = 10)
str(PCIS_LE)

PCIS_LE$PCIS_final <- as.numeric(PCIS_LE$PCIS_final)
PCIS_LE$Chla       <- as.numeric(PCIS_LE$Chla)
PCIS_LE$temp       <- as.numeric(PCIS_LE$temp)
PCIS_LE$plot       <- as.factor(PCIS_LE$plot)
PCIS_LE$site       <- as.factor(PCIS_LE$site)

PCIS_LE <- PCIS_LE[!is.na(PCIS_LE$PCIS_final),]## exclude NAs

str(PCIS_LE)
hist(PCIS_LE$PCIS_final)

#### *** Verify homogeneity of variances per stratum *** ####
a0 <- gls(PCIS_final ~ Chla + temp, method = "REML", data = PCIS_LE)
plot(a0)## Evidence of unequal variances ##

a1 <- gls(PCIS_final ~ Chla + temp, method = "REML", weights = varPower(form=~ Chla), data = PCIS_LE)
a2 <- gls(PCIS_final ~ Chla + temp, method = "REML", weights = varPower(form=~ temp), data = PCIS_LE)
a3 <- gls(PCIS_final ~ Chla + temp, method = "REML", weights = varExp(form=~ Chla), data = PCIS_LE)
a4 <- gls(PCIS_final ~ Chla + temp, method = "REML", weights = varIdent(form=~ 1|site), data = PCIS_LE)

m <- list(a0, a1, a2, a3, a4) ## list of models under comparison ##
modnames.m <- c("a0", "a1", "a2", "a3", "a4") ## naming different models ##
AICctab(m, mnames = modnames.m, base = TRUE, weights = TRUE, logLik = TRUE) ## AICc tab ##

anova(a0, a4)
plot(a4)
## Result: heterocedasticity; therefore consider model that account for that ##

#### *** LMM: pcis ~ prey density*wave exposure and random effect of site *** ####
m.pcis2a <- lme(PCIS_final ~ Chla + temp, random = ~1|site, data = PCIS_LE)
plot(m.pcis2a)## not OK ##

m.pcis <- lme(PCIS_final ~ Chla + temp, random = ~1|site, weights = varIdent(form=~ 1|site), data = PCIS_LE)

plot(resid(m.pcis, type = "normalized") ~ fitted(m.pcis)) ## OK ##
plot(resid(m.pcis, type = "normalized") ~ PCIS_LE$Chla) ## OK ##
plot(resid(m.pcis, type = "normalized") ~ PCIS_LE$temp) ## OK ##

summary(m.pcis)
VarCorr(m.pcis)
hist(resid(m.pcis, type = "normalized"))

m.pcisML  <- lme(PCIS_final ~ Chla + temp, random = ~1|site, data = PCIS_LE, weights = varIdent(form=~ 1|site), method = "ML")
m.pcisML2 <- lme(PCIS_final ~ Chla, random = ~1|site, data = PCIS_LE, weights = varIdent(form=~ 1|site), method = "ML")

anova(m.pcisML, m.pcisML2)

m.pcisML3 <- lme(PCIS_final ~ temp, random = ~1|site, data = PCIS_LE, varIdent(form=~ 1|site), method = "ML")
anova(m.pcisML, m.pcisML3)

## FINAL MODEL: PCIS_final ~ CHLA + TEMPERATURE; NO EFFECT OF ANY FACTOR ##
summary(m.pcis)
VarCorr(m.pcis)

## Model for: PCIS ~ long ##
m.long <- lme(PCIS_final ~ long, random = ~1|site, weights = varIdent(form=~ 1|site), data = PCIS_LE)

summary(m.long)
plot(m.long)
hist(residuals(m.long))
VarCorr(m.long)
```


## Predictions of PCIS LMM ##
```{r predictions PCIS}

#### Predictions for Chla ####
PCIS_LE_pred       <- PCIS_LE ## Dataframe for predictions ##
PCIS_LE_pred       <- subset(PCIS_LE_pred, select = c(2, 6, 7, 16)) ## keep only useful columns ##
PCIS_LE_pred$Chla2 <- as.character(PCIS_LE_pred$Chla) ## create character column to match ##

mydf = ggpredict(m.pcis, terms = c("Chla", "temp"))
names(mydf) <- c("Chla", "predicted", "sd", "low", "high", "temp") ## renaming output ##
mydf$Chla2 = as.character(mydf$Chla)

PCIS_LE_pred$predicted  <- mydf$predicted[match(as.character(PCIS_LE_pred$Chla2), as.factor(mydf$Chla2))]
PCIS_LE_pred$low        <- mydf$low[match(as.character(PCIS_LE_pred$Chla2), as.factor(mydf$Chla2))]
PCIS_LE_pred$high       <- mydf$high[match(as.character(PCIS_LE_pred$Chla2), as.factor(mydf$Chla2))]

pred1 <-
ggplot(PCIS_LE_pred, aes(x = Chla, y = PCIS_final)) +
     geom_ribbon(aes(ymin = low, ymax = high), alpha = .3) +
     scale_fill_manual(values=c("grey75", "grey75")) +
     geom_line(aes(y = predicted), size = 1.1) +
     #scale_linetype_manual(values= c("solid", "longdash"))+
     geom_point(size= 2.5, alpha=0.95) + 
     scale_shape_manual(values=c(15))+
     scale_color_manual(values=c('black')) +
     theme_classic() +
     theme(axis.text.x = element_text(size=14, color="black"), 
           axis.text.y = element_text(size=14, color="black"),
           axis.title.x = element_text(color="black", size=16.),
           axis.title.y = element_text(color="black", size=16)) +
     labs(x = expression(paste("satellite Chla (mg.m"^-3,")")),
          y = "PCIS") +
     theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
     theme(axis.line = element_line(colour = 'black', size = 0.8)) +
     theme(axis.ticks.length = unit(4, "pt")) +
     theme(legend.position = c(.02, .93),
           legend.justification = c("left"),
           legend.box.just = "left",
           legend.margin = margin(0, 0, 0, 0),
           legend.key.size = unit(1.5,"line")) +
     theme(legend.title = element_text(color = "white", size = 5),
           legend.text = element_text(color = "black", size=11))#+
      #expand_limits(x=c(0,5)) + xlim(0.8, 5.0)
     #scale_x_continuous(breaks = seq(0, 5))

pred1

rm(mydf, PCIS_LE_pred)

### Predictions for temperature ###

PCIS_LE_pred       <- PCIS_LE ## Dataframe for predictions ##
PCIS_LE_pred       <- subset(PCIS_LE_pred, select = c(2, 6, 7, 16)) ## keep only useful columns ##
PCIS_LE_pred$temp2 <- as.character(PCIS_LE_pred$temp) ## create character column to match ##

mydf        <- ggpredict(m.pcis, terms = c("temp", "Chla"))
names(mydf) <- c("temp", "predicted", "sd", "low", "high", "Chla") ## renaming output ##
mydf$temp2  <- as.character(mydf$temp)

PCIS_LE_pred$predicted  <- mydf$predicted[match(as.character(PCIS_LE_pred$temp2), as.factor(mydf$temp2))]
PCIS_LE_pred$low        <- mydf$low[match(as.character(PCIS_LE_pred$temp2), as.factor(mydf$temp2))]
PCIS_LE_pred$high       <- mydf$high[match(as.character(PCIS_LE_pred$temp2), as.factor(mydf$temp2))]

pred2 <-
ggplot(PCIS_LE_pred, aes(x = temp, 
                         y = PCIS_final)) +
     geom_ribbon(aes(ymin = low, 
                     ymax = high), 
                 alpha = .3) +
     scale_fill_manual(values=c("grey75", 
                                "grey75")) +
     geom_line(aes(y = predicted), 
               size = 1.1) +
     #scale_linetype_manual(values= c("solid", "longdash"))+
     geom_point(size= 2.5, 
                alpha=0.95) + 
     scale_shape_manual(values=c(15))+
     scale_color_manual(values=c('black')) +
     theme_classic() +
     theme(axis.text.x = element_text(size=14, 
                                      color="black"), 
           axis.text.y = element_text(size=14, 
                                      color="black"),
           axis.title.x = element_text(color="black", 
                                       size=16.),
           axis.title.y = element_text(color="black", 
                                       size=16)) +
        labs(x = expression(paste("sea temperature (°C)")),
          y = "PCIS") +
     theme(axis.ticks = element_line(colour = "black", 
                                     size = 0.8)) +
     theme(axis.line = element_line(colour = 'black', 
                                    size = 0.8)) +
     theme(axis.ticks.length = unit(4, "pt")) +
     theme(legend.position = c(.02, .93),
           legend.justification = c("left"),
           legend.box.just = "left",
           legend.margin = margin(0, 0, 0, 0),
           legend.key.size = unit(1.5,"line")) +
     theme(legend.title = element_text(color = "white", 
                                       size = 5),
           legend.text = element_text(color = "black", 
                                      size=11))+
     theme(plot.margin=unit(c(0.2, 1, 0.2, 0.2), "cm"))

pred2

ggarrange(pred1, pred2, ncol = 2, nrow = 1, align = "hv")
#ggsave("pcis-exp02.svg", dpi = 400, width = 12.5, height = 3.57, units = "in") ## Okay
```


## Residuals for PCIS model: PCIS ~ Chla + SST ##
```{r}

res.pcis1 <- residuals(m.pcis, type = "normalized") ## to get residuals of the model ##
fit.pcis1 <- fitted(m.pcis)                         ## to get fitted values  of the model ##

res.pcis1 <- cbind(res.pcis1, fit.pcis1) ## binding columns ##
res.pcis1 <- as.data.frame(res.pcis1) ## transforming object in dataframe ##

res.pcis1$Chla <- PCIS_LE$Chla ## getting column Chla from dataframe with same length ##
res.pcis1$temp <- PCIS_LE$temp ## getting column temp from dataframe with same length ##

res.1 <-
  ggplot(res.pcis1, aes(x=fit.pcis1, y=res.pcis1)) + theme_linedraw() + 
  geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "fitted values", 
       y = "normalised residuals") +
  theme(strip.text.x = element_text(size = 12), 
        strip.text.y = element_text(size = 12))+
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(0.15,0.30,0.15,.15), "lines")) +
  theme(strip.text.x = element_text(size = 10), 
        strip.text.y = element_text(size = 10))+
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))+
  scale_x_continuous(breaks = seq(from = -0.0015, to = 0.0005, by = 0.0005))

res.2 <-
  ggplot(res.pcis1, aes(x= Chla, y=res.pcis1)) + theme_linedraw()+ 
  geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "Chla", y = "normalised residuals") +
  theme(strip.text.x = element_text(size = 12), 
        strip.text.y = element_text(size = 12))+
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(0.15,0.15,.3,.15), "lines")) +
  theme(strip.text.x = element_text(size = 10), 
        strip.text.y = element_text(size = 10))+
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.3 <- 
  ggplot(res.pcis1, aes(x= temp, y=res.pcis1)) + theme_linedraw()+ 
  geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "temperature", y = "normalised residuals") +
  theme(strip.text.x = element_text(size = 12), 
        strip.text.y = element_text(size = 12))+
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(0.15,0.15,.3,.15), "lines")) +
  theme(strip.text.x = element_text(size = 10), 
        strip.text.y = element_text(size = 10))+
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.4 <- 
  ggplot(res.pcis1, aes(x=res.pcis1)) + geom_histogram(color="black", fill="white", bins=8)+ 
  theme_linedraw()+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "normalised residuals", y = "count") +
  theme(strip.text.x = element_text(size = 12), 
        strip.text.y = element_text(size = 12))+
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(1.2,0.15,0.15,.15), "lines")) +
  theme(strip.text.x = element_text(size = 10), 
        strip.text.y = element_text(size = 10))+
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

r.pcis <- ggarrange(res.1, res.2, res.3, res.4, ncol = 2, nrow = 2, align = "hv")
r.pcis <- annotate_figure(r.pcis, fig.lab = "PCIS", fig.lab.face = "bold", fig.lab.size=12)
r.pcis

#ggsave("residuals-pcis-exp02.png", dpi = 300, width = 5.82, height = 6.01, units = "in")
```


## CONSUMPTION RATE ~ Chla + SST ##
```{r consumption rate}

exp2019 <- read_excel("Pardal-2021-data-Exp-02.xlsx", sheet = 11)
str(exp2019)

exp2019$consRate <- as.numeric(exp2019$consRate)
exp2019$Chla     <- as.numeric(exp2019$Chla)
exp2019$temp     <- as.numeric(exp2019$temp)
exp2019$plot     <- as.factor(exp2019$plot)
exp2019$site     <- as.factor(exp2019$site)

hist(exp2019$consRate) 

exp2019b <- exp2019[!is.na(exp2019$consRate),] ## exclude NAs ##

## important: consRate negatives values turned to 0 (there cannot be negative consumprion rate):##
exp2019b$consRate[exp2019b$consRate < 0] = 0

b0 <- gls((consRate) ~ Chla + temp, method = "REML", data = exp2019b)
plot(b0)## Evidence of unequal variances ##

b1 <- gls(consRate ~ Chla + temp, method = "REML", weights = varPower(form= ~ Chla), data = exp2019b)
b2 <- gls(consRate ~ Chla + temp, method = "REML", weights = varPower(form= ~ temp), data = exp2019b)
b3 <- gls(consRate ~ Chla + temp, method = "REML", weights = varExp(form= ~ Chla), data = exp2019b)
b4 <- gls(consRate ~ Chla + temp, method = "REML", weights = varIdent(form= ~ 1|site), data = exp2019b)

m1 <- list(b0, b1, b2, b3, b4) ## list of models under comparison ##
modnames.m1 <- c("b0", "b1", "b2", "b3", "b4") ## naming different models ##
AICctab(m1, mnames = modnames.m1, base = TRUE, weights = TRUE, logLik = TRUE) ## AICc tab ##
## Equal variances ##

m.cons <- lme(consRate ~ Chla + temp, random = ~1|site, data = exp2019b)
summary(m.cons)
VarCorr(m.cons)

plot(m.cons)
hist(resid(m.cons))

m.cons2 <- lme(consRate ~ Chla, random = ~1|site, data = exp2019b)
summary(m.cons2)

m.cons3 <- lme(consRate ~ temp, random = ~1|site, data = exp2019b)
summary(m.cons3)

## Testing for spatial pattern in Consumption rate (~ longitude) ##
m.long2 <- lme(consRate ~ long, random = ~1|site, weights = varIdent(form = ~ 1|site), data = exp2019b)

summary(m.long2)
plot(m.long2)
hist(residuals(m.long2))
VarCorr(m.long2)
``` 


### Predictions: consumption rate ~ Chla + SST ##
```{r predictions consumption}

#### Predictions for Chla ####
exp2019_pred       <- exp2019b ## Dataframe for predictions ##
exp2019_pred       <- subset(exp2019_pred, select = c(2, 6, 7, 16)) ## keep only useful columns ##
exp2019_pred$Chla2 <- as.character(exp2019_pred$Chla) ## create character column to match ##

mydf        <- ggpredict(m.cons, terms = c("Chla", "temp"))
names(mydf) <- c("Chla", "predicted", "sd", "low", "high", "temp") ## renaming output ##
mydf$Chla2  <- as.character(mydf$Chla)

exp2019_pred$predicted  <- mydf$predicted[match(as.character(exp2019_pred$Chla2), as.factor(mydf$Chla2))]
exp2019_pred$low        <- mydf$low[match(as.character(exp2019_pred$Chla2), as.factor(mydf$Chla2))]
exp2019_pred$high       <- mydf$high[match(as.character(exp2019_pred$Chla2), as.factor(mydf$Chla2))]

pred3 <-
ggplot(exp2019_pred, aes(x = Chla,
                         y = consRate)) +
     geom_ribbon(aes(ymin = low, ymax = high), 
                 alpha = .3) +
     scale_fill_manual(values=c("grey75", "grey75")) +
     geom_line(aes(y = predicted), 
               size = 1.1) +
     geom_point(size= 2.5, 
                alpha=0.95) + 
     scale_shape_manual(values=c(15))+
     scale_color_manual(values=c('black')) +
     theme_classic() +
     theme(axis.text.x = element_text(size=14, color="black"), 
           axis.text.y = element_text(size=14, color="black"),
           axis.title.x = element_text(color="black", size=16.),
           axis.title.y = element_text(color="black", size=16)) +
     labs(x = expression(paste("satellite Chla (mg.m"^-3,")")),
          y = expression(atop("consumption rate", paste("(barnacles .dogwhelk"^-1, ".day"^-1,")")))) +
     theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
     theme(axis.line = element_line(colour = 'black', size = 0.8)) +
     theme(axis.ticks.length = unit(4, "pt")) +
     theme(legend.position = c(.02, .93),
           legend.justification = c("left"),
           legend.box.just = "left",
           legend.margin = margin(0, 0, 0, 0),
           legend.key.size = unit(1.5,"line")) +
     theme(legend.title = element_text(color = "white", size = 5),
           legend.text = element_text(color = "black", size=11))+
     theme(plot.margin=unit(c(0.2, 1, 0.2, 0.2), "cm"))   

pred3

rm(mydf, exp2019_pred)

### Predition for temperature ###

exp2019_pred       <- exp2019b ## Dataframe for predictions ##
exp2019_pred       <- subset(exp2019_pred, select = c(2, 6, 7, 16)) ## keep only useful columns ##
exp2019_pred$temp2 <- as.character(exp2019_pred$temp) ## create character column to match ##

mydf        <- ggpredict(m.cons, terms = c("temp", "Chla"))
names(mydf) <- c("temp", "predicted", "sd", "low", "high", "Chla") ## renaming output ##
mydf$temp2  <-as.character(mydf$temp)

exp2019_pred$predicted  <- mydf$predicted[match(as.character(exp2019_pred$temp2), as.factor(mydf$temp2))]
exp2019_pred$low        <- mydf$low[match(as.character(exp2019_pred$temp2), as.factor(mydf$temp2))]
exp2019_pred$high       <- mydf$high[match(as.character(exp2019_pred$temp2), as.factor(mydf$temp2))]

pred4 <-
ggplot(exp2019_pred, aes(x = temp, 
                         y = consRate)) +
     geom_ribbon(aes(ymin = low, ymax = high), 
                 alpha = .3) +
     scale_fill_manual(values=c("grey75", "grey75")) +
     geom_line(aes(y = predicted), size = 1.1) +
     geom_point(size= 2.5, 
                alpha=0.95) + 
     scale_shape_manual(values=c(15))+
     scale_color_manual(values=c('black')) +
     theme_classic() +
     theme(axis.text.x = element_text(size=14, color="black"), 
           axis.text.y = element_text(size=14, color="black"),
           axis.title.x = element_text(color="black", size=16.),
           axis.title.y = element_text(color="black", size=16)) +
        labs(x = expression(paste("temperature (°C)")),
          y = expression(atop("consumption rate", paste("(barnacles .dogwhelk"^-1, ".day"^-1,")")))) +
     theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
     theme(axis.line = element_line(colour = 'black', size = 0.8)) +
     theme(axis.ticks.length = unit(4, "pt")) +
     theme(legend.position = c(.02, .93),
           legend.justification = c("left"),
           legend.box.just = "left",
           legend.margin = margin(0, 0, 0, 0),
           legend.key.size = unit(1.5,"line")) +
     theme(legend.title = element_text(color = "white", size = 5),
           legend.text = element_text(color = "black", size=11))+
     theme(plot.margin=unit(c(0.2, 1, 0.2, 0.2), "cm"))  

pred4

ggarrange(pred3, pred4, pred1, pred2, ncol = 2, nrow = 2, align = "hv")
#ggsave("predictions-large-scale-final.svg", dpi = 400, width = 12.70, height = 8.67, units = "in")
##Saving 12.7 x 8.67 in image##
```


## Residuals for consumption rate model: PCIS ~ Chla + SST ##
```{r Residuals for ConsRate model}

res.cons1 <- residuals(m.cons, type = "normalized") ## to get residuals of the model ##
fit.cons1 <- fitted(m.cons) ## to get fitted valies  of the model ##

res.cons1 <- cbind(res.cons1, fit.cons1) ## binding columns ##
res.cons1 <- as.data.frame(res.cons1) ## transforming objetc in dataframe ##

res.cons1$Chla <- exp2019b$Chla ## getting column time from dataframe with same length ##
res.cons1$temp <- exp2019b$temp ## getting column time from dataframe with same length ##

res.1 <-
  ggplot(res.cons1, aes(x=fit.cons1, y=res.cons1)) + theme_linedraw()+ 
  geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "fitted values", y = "normalised residuals") +
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(0.15,0.30,0.15,.15), "lines")) +
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.2 <-
  ggplot(res.cons1, aes(x= Chla, y=res.cons1)) + theme_linedraw()+ 
  geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "Chla", y = "normalised residuals") +
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(0.15,0.15,.3,.15), "lines")) +
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.3 <- 
  ggplot(res.cons1, aes(x= temp, y=res.cons1)) + theme_linedraw()+ 
  geom_point(size=2.5, alpha=0.7, colour="black")+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "temperature", 
       y = "normalised residuals") +
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(0.15,0.15,.3,.15), "lines")) +
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

res.4 <-
  ggplot(res.cons1, aes(x=res.cons1)) + 
  geom_histogram(color="black", fill="white", bins=9) + theme_linedraw()+
  theme(axis.text.x = element_text(size=12, color="black"), 
        axis.text.y = element_text(size=12, color="black"),
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "normalised residuals", 
       y = "count") +
  theme(legend.position = "none") + 
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))+ 
  theme(plot.margin = unit(c(1.2,0.15,0.15,.15), "lines")) +
  theme(panel.background = element_rect(fill = "white",colour = "black", size = 1.0, linetype = "solid"),
        panel.grid.major = element_line(size = .5, linetype = 'solid',colour = "gray95"), 
        panel.grid.minor = element_line(size = .5, linetype = 'solid',colour = "gray95"))

r.cons <- ggarrange(res.1, res.2, res.3, res.4, ncol = 2, nrow = 2, align = "hv")
r.cons <- annotate_figure(r.cons, fig.lab = "consumption rate", fig.lab.face = "bold", fig.lab.size=12)
r.cons

#ggsave("RES-CR-Exp2-Rev.png", dpi = 300, width = 5.82, height = 6.01, units = "in")
```


## Initial prey density in +P and -P treatment (Fig. 2 in the manuscript) ##
```{r Prey density time 0}

tetra_density <- read_excel("Pardal-2021-data-Exp-02.xlsx", sheet = 2)
str(tetra_density)

tetra_density <- as.data.frame(subset(tetra_density, (day == "0")))

tetra_density$preyNumber <- as.numeric(tetra_density$preyNumber)
tetra_density$site       <- as.factor(tetra_density$site)
tetra_density$predator   <- as.factor(tetra_density$predator)
tetra_density$predTreat  <- as.factor(tetra_density$predTreat)

str(tetra_density)

tetra_density2 <- tetra_density[!is.na(tetra_density$preyNumber),] ## exclude NAs ##

## for plotting the global mean line ###dt2 =  ddply(tetra_density2, "predator", transform, 
       #prey_mean  = mean(preyNumber)) 

tetra_density2$site <- factor(tetra_density2$site, 
                              levels = c("Astúrias", "Iporanga", "Itassucê", "Zimbro", 
                                         "P. Vermelha", "P. Grande", "Grumari", 
                                         "Piratininga","Fortaleza", "Prainha"))

tetra_density2$predator <- factor(tetra_density2$predator, 
                             levels = c("−P", "+P"))

barnacle_density2 <- 
  ggplot(tetra_density2, aes(x = predator, 
                             y = preyNumber, 
                             group = site))+ 
  theme_classic() +
  #geom_jitter(position=position_jitter(0.02), 
             #size=2.3, 
             #alpha=0.2) + 
  #geom_hline(aes(yintercept = prey_mean), 
             #colour = 'gray', 
            # linetype="dashed",
             #size=1.2)+
  stat_summary(fun.data="mean_se",  
               fun.args = list(mult=1),
               geom="pointrange", 
               color = "black", 
               size=1.3)+
  facet_grid(~ site, scale='free_y') +
  theme(axis.text.x = element_text(size=12, color="black"),
        axis.text.y = element_text(size=12, color="black"), 
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "treatment", 
       y = expression(paste("number of barnacles (ind.625 cm"^-2,")")))+
  theme(strip.text.x = element_text(size = 12), 
        strip.text.y = element_text(size = 12))+
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))

barnacle_density2 

#ggsave("figs-rev/Oecologia-LE-density_initial.svg", dpi = 400, width = 11.2, height = 3.8, units="in") 
```


## Background mortality ##
```{r Background mortality}

nat_mortality <- read_excel("Pardal-2021-data-Exp-02.xlsx", sheet= 9)
str(nat_mortality)

nat_mortality$site <- as.factor(nat_mortality$site)
#nat_mortality$mortality = (nat_mortality$Bo) - (nat_mortality$Bt)

str(nat_mortality)

mort <- aggregate(mortNat ~ site, mean, data = nat_mortality)
summary(nat_mortality)

nat_mortality$site <- factor(nat_mortality$site, 
                             levels = c("Astúrias", "Iporanga", "Itassucê", "Zimbro", 
                                        "P. Vermelha", "P. Grande", "Grumari", 
                                        "Piratininga","Fortaleza", "Prainha"))

exp2_back <-
  ggplot(nat_mortality, aes(y = mortNat, 
                            x = site))+ 
  theme_classic() +
  geom_point(size=2.3, 
             alpha=0.2) + 
    stat_summary(fun.data="mean_se",  
               fun.args = list(mult=1),
               geom="pointrange", 
               color = "black", 
               size=1.3)+
  theme(axis.text.x = element_text(size=12, color="black", 
                                   angle= 90, 
                                   vjust = 0.5, 
                                   hjust = 1),
        axis.text.y = element_text(size=12, color="black",), 
        axis.title.x = element_text(color="black", size=14),
        axis.title.y = element_text(color="black", size=14))+
  labs(x = "site", 
       y = expression(atop("background mortality rate ", 
                          paste("(barnacles.day"^-1,")")))) +
  theme(strip.text.x = element_text(size = 12), 
        strip.text.y = element_text(size = 12))+
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) +
  theme(axis.line = element_line(colour = 'black', size = 0.8)) +
  theme(axis.ticks.length = unit(4, "pt"))


back_mortality <- ggarrange(gexp1_back, exp2_back, ncol = 1, nrow = 2, align = "hv")
back_mortality

#ggsave("figs-rev/back-mortality1-2.svg", dpi = 300)
```


## Plotting spatial patterns (ESM: Appendix A, Fig. A6) ##
```{r PCIS and ConsRate ~ latitude and longitude}

exp2019b$site  <- factor(exp2019b$site , 
                        levels = c("Astúrias", "Iporanga", "Itassucê", 
                                   "Zimbro", "P. Vermelha", "P. Grande", 
                                   "Grumari", "Piratininga","Fortaleza", 
                                   "Prainha"))

spt01 <-  
  ggplot(exp2019b, aes(y= consRate, x= long))+ 
  geom_jitter(height = 0, 
             width = 0.05, 
             size=2.3, 
             alpha=0.25) + 
  stat_summary(fun.data = "mean_se",  
               fun.args = list(mult=1), 
               geom = "pointrange", 
               size=1.7)+
  theme_classic() + 
  theme(axis.text.x = element_text(size = 16, 
                                   color = "black"), 
                                   #angle = 90, 
                                   #vjust = 0.5, 
                                   #hjust = 1), 
         axis.text.y = element_text(size = 16, 
                                     color = "black"),
         axis.title.x = element_text(color = "black", 
                                      size = 16),
         axis.title.y = element_text(color="black", 
                                      size=16))+ 
  labs(x = "", 
      y = expression(atop("consumption rate", 
                          paste("(barnacles .dogwhelk"^-1, ".day"^-1,")")))) +
  scale_color_manual(values=c('black','red'))+ 
  theme(strip.text.x = element_text(size = 12), 
        strip.text.y = element_text(size = 12))+ 
  theme(legend.position = "none") +
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) + 
  theme(axis.line = element_line(colour = 'black', size = 0.8)) + 
  theme(axis.ticks.length = unit(4, "pt"))

spt01

spt02 <-  
  ggplot(PCIS_LE, aes(y= PCIS_final, x = long))+ 
  geom_jitter(height = 0, 
             width = 0.05, 
             size=2.3, 
             alpha=0.25) + 
  stat_summary(fun.data = "mean_se",  
               fun.args = list(mult=1), 
               geom = "pointrange", 
               size=1.7)+
  theme_classic() + 
  theme(axis.text.x = element_text(size = 16, 
                                   color = "black"), 
                                   #angle = 90, 
                                   #vjust = 0.5, 
                                   #hjust = 1), 
         axis.text.y = element_text(size = 16, 
                                     color = "black"),
         axis.title.x = element_text(color = "black", 
                                      size = 16),
         axis.title.y = element_text(color="black", 
                                      size=16))+ 
  labs(x = "longitude", 
      y = "PCIS") +
  scale_color_manual(values=c('black','red'))+ 
  theme(strip.text.x = element_text(size = 12), 
        strip.text.y = element_text(size = 12))+ 
  theme(legend.position = "none") +
  theme(axis.ticks = element_line(colour = "black", size = 0.8)) + 
  theme(axis.line = element_line(colour = 'black', size = 0.8)) + 
  theme(axis.ticks.length = unit(4, "pt"))

spt02

ggarrange(spt01, spt02, ncol = 1, nrow = 2, align = "hv")
#ggsave("spatial-plot-final.svg", dpi = 300) #width = 195, height = 195, units = "mm") ## Okay
```
